A non-additive generalization of probability theory \\for quantum mechanics and beyond

### 2025-07-15 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex
NonAdditiveProbability: adding some literature for non-additive measures

@@

\textbf{Quick overview of the literature.}

\textbf{A test case for the Choquet integral.} We are now going to compute the Choquet integral for a two state quantum system and see that, unfortunately, it does not recover the expectation of the statistical variables in the corresponding ensemble space.

>>>>

One important feature, for example, would be to characterize what fraction capacities are possible for each ensembles space. In the classical case, for example, only additive fraction capacities are possible; in the quantum case, only some type of non-additivity will be possible. The shape of the space effectively is encoded in the space of possible fraction capacities, maybe in a way that is mathematically and physically insightful.

@@

\textbf{Ruling out Sugeno and Choquet integrals.} Non-additive measures are used in disparate contexts, such as game theory, economic decision theory, optimization and artificial intelligence. CITE To our knowledge, there isn't a single unified theory, though some work has been proceeding in that direction.\cite{nonadditive2014,pap2013} For now, we will concentrate on integration. The Choquet integral and the Sugeno integral are the oldest and most common approaches to integration of non-additive measure, and therefore we should first test whether these work.

Note that the Sugeno integral does not recover the Lebesgue integral in the case the capacity is additive (i.e. classical), and is therefore ruled out. The Choquet integral does, so it will work in the classical case. However, it does not work in the quantum case. We can show this by computing the Choquet integral for a two states quantum system and see that it does not recover the expectation of the statistical variables in the corresponding ensemble space.
